\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

% added
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{dblfloatfix}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\newcommand{\sysname}{X-Monitor}

\title{{\sysname}: XDP-based Lightweight Monitoring \\ for Cloud-native Services}

% \author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% \and
% \IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% \and
% \IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% \and
% \IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% \and
% \IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% \and
% \IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% }

\maketitle

\begin{abstract}
Cloud-native services have evolved from monolithic architectures to microservices, comprising hundreds to thousands of containerized components.  
These microservices are launched frequently and collaborate closely, and each must meet strict requirements for responsiveness and availability.
To satisfy service-level agreements (SLAs), monitoring plays a critical role in microservices. 
To enable an orchestration system to manage each microservice effectively, monitoring services must operate with both low latency and low overhead, allowing them to capture timely service status without compromising service performance.
However, conventional user-space monitoring tools such as Netdata and Prometheus incur scheduling delays and context switch overhead, resulting in increased monitoring latency and degraded service performance.

We present X-Monitor, a lightweight monitoring framework based on eXpress Data Path (XDP).  
X-Monitor has three key features:  
(1) In-kernel monitoring achieves low overhead by eliminating user-kernel context switches, as both packet processing and metric collection are performed entirely within the kernel.  
(2) SoftIRQ-level execution enables low-latency monitoring by reducing delay in executing these monitoring tasks without incurring scheduling latency and with minimal preemption.
(3) Programmable metric selection enables flexible in-kernel monitoring via user-defined XDP programs.
Our evaluation using Memcached and YCSB demonstrates that X-Monitor reduces the 99.9th percentile monitoring latency by two orders of magnitude and mitigates throughput degradation by up to 11.8\% compared to traditional monitoring systems.
\end{abstract}

\begin{IEEEkeywords}
% component, formatting, style, styling, insert
\end{IEEEkeywords}

\input{Introduction}
\input{Background}
\input{Proposal}
\input{Design-Implementation}
% \input{CaseStudy}
\input{Evaluation}
\input{Relatedwork}
\input{Conclusion}

\bibliographystyle{IEEEtran}
\bibliography{reference}

\end{document}
